Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-06 papers/ms.tex
improve phased lc layout
paper: add bad intro

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,tighten]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia
  are yielding a refined view of stellar clusters during the
  first hundred million years of their lives.
  Here we present an analysis of a group of $38 \pm 6$ million year old stars
  spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$), hereafter the Cep-Her complex.
  This group of stars includes four previously known Kepler Objects of
  Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a component of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the latter three
  systems, which are in other sub-components of the complex (RSG-5 and
  CH-2).  Based on kinematic evidence from Gaia, stellar rotation
  periods from TESS, and spectroscopy, these three systems are also
  $38 \pm 6$ million years old.  Based on the transit shapes and high
  resolution imaging, we statistically validate that they are all most
  likely planets (false positive probabilities of $6\times10^{-9}$,
  $5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively).  Supplemented by Gaia and TESS, the main
  Kepler mission is now contributing to the census of young close-in
  planets, and Kepler-1643 and KOI-7913 are the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of roughly 40 million years.
\end{abstract}

@@

@@

@@

\subsection{Kepler\,1627A}
\subsection{Kepler\,1643}
\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.99\textwidth]{f3e.pdf}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3a.pdf}
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
			\includegraphics[width=0.5\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Raw and processed light curves for the objects of
    interest.} Top: raw.  Bottom: processed.
    There increases scatter during transit is likely due to starspot
    crossing events.
		\label{fig:planets}
	}
\end{figure*}

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,twocolumn,linenumbers]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of stellar cluster evolution.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.  The group contains
  four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the latter three
  systems, which are in other sub-components of the complex (RSG-5 and
  CH-2).  Based on kinematic evidence from Gaia, stellar rotation
  periods from TESS, and spectroscopy, these three systems are also
  $38 \pm 6$ million years old.  Based on the transit shapes and high
  resolution imaging, they are all most
  likely planets (false positive probabilities of $6\times10^{-9}$,
  $5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively).  Kepler-1643 and KOI-7913 are therefore
  the first empirical demonstration that mini-Neptunes with sizes of
  $\approx$2 Earth radii exist at ages of roughly 40 million years.
\end{abstract}

@@

The discovery of young transiting planets is a major frontier in
current exoplanet research.  The reason is that the properties of
these planets can help constrain the timescales for processes
including hot Jupiter migration (CITE), the cooling and contraction of
mini-Neptunes (CITE Rizzuto), the early evolution of close-in
multiplanet systems (CITE David), and whether and how mass-loss
explains the radius valley (e.g., CITE, CITE, Lee+21 on theory; CITE
CITE CITE on observations).

Assuming a constant star formation rate in the Galaxy, $\approx$1\% of
stars are $\lesssim$10$^8$ years old.  While $\approx$5{,}000
transiting exoplanets are known (CITE), 11 currently meet this age
cut.  The discrepancy between the $\approx$50 expected and $\approx$10
known likely has a contribution from selection effects in planetary
detection, which include photometric and spectroscopic starspot
modulation, and the rarity of young stars.

While detecting planets around young and active stars is challenging,
so is measuring stellar ages (see CITE Soderblom for a review).  It
should therefore not be surprising that advances along either
dimension can yield advances in the census of young transiting
planets.

The prime Kepler mission (CITE) found most of the currently known
transiting exoplanets, and it was conducted before the positions,
velocities, and stellar brightnesses measured by Gaia revolutionized
our understanding of stellar clusters (CITE, CITE, CITE).  This
revolution is slated to continue with the upcoming third Gaia data
release (DR3 CITE).  Nonetheless, it seems sensible to revisit the
Kepler field, given our new knowlege of the stellar ages.

In this work, we expand on a previous study of a 38 million year (Myr)
old Neptune-sized planet in the Kepler field (Kepler-1627Ab; CITE).
The age of this planet was derived based on its host star's membership
in the $\delta$\ Lyr\ cluster.  Our analysis of this cluster focused
on the immediate kinematic vicinity of Kepler-1627A in order to
reliably confirm the age of the planet.  However it also became clear
that the $\delta$\ Lyr\ cluster is spatially and kinematically close
to a much larger group of similarly aged stars.  This group, which is
at a distance of roughly 300 parsecs, appears to span Cepheus
($l=100^\circ$) to Hercules ($l=40^\circ$), at galactic latitudes,
$b$, between roughly 0 and 20 degrees.  We therefore refer to it as
the Cep-Her complex.  Viewed top-down in the plane of the Galaxy, the
complex spans roughly 250 parsecs in the direction toward the galactic
center, and 150 parsecs in the perpendicular direction of galactic
rotation.  A detailed kinematic analysis and exploration is currently
being prepared by R.~Kerr and collaborators.

The subject of this study is the intersection of the Cep-Her complex
with the Kepler field, and an analysis of the consequent transiting
planets and planet candidates.  Cross-matching the full set of
candidate Cep-Her members against all known Kepler Objects of Interest
(CITE) yielded XX candidate matches.  Given the purported XX Myr age
of the group, a visual inspection of the light curves quickly enabled
a decision about whether the matches could be valid, based on the
presence or non-presence of stellar rotation signals of the
appropriate periods and amplitudes (CITE REBULL).  Four possible
matches remained from this exercise: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.  Given our previous analysis of Kepler-1627,
we will focus for the most part on the latter three.

@@

The evidence for the RSG-5 and CH-2 sub-groups at least roughly
sharing the age of the $\delta$\ Lyra\ cluster is shown in
Figure~\ref{fig:age}.

@@

\input{tab_sysparams.tex}

Many of the relevant stellar parameters can be gleaned by inspecting
Figure~\ref{fig:age}.  The known planet-hosting stars in Cep-Her span
spectral types of G8V (Kepler-1627) to K8V (KOI-7913 A).  The
secondary in the KOI-7913 system is only marginally cooler than the
primary (SpType $\approx$M0V).
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO
A Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ million years (CITE CHOI MESA), and so these
stars are in the end stages of their pre-main-sequence contraction.
Their Gaia EDR3 parallaxes span X.X to Y.Y, corresponding to distances
between X.X and Y.Y parsecs.

To derive the spectroscopic parameters $(T_{\rm eff}, \log g_\star,
[{\rm Fe/H}])$ and  the equivalent width of the Li\,\textsc{I}
from the 6708\,\AA\ doublet, we acquired spectra.  Specifically, we
acquired iodine-free HIRES spectra for Kepler-1643 (YYYY/MM/DD) and
KOI-7913 (YYYY/MM/DD and YYYY/MM/DD), where for the latter the two
different epochs corresponded to observations of the secondary and
primary respectively.  The acquisition and analysis followed the
standard reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  For KOI-7368, we acquired TRES spectra on
YYYY/MM/DD and YYYY/MM/DD.  CITE METHOD PAPER.
The results are given in Table~\ref{tab:sysparams}.

Table~\ref{tab:sysparams} summarizes
%
%from the 
%
%
%\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
%spectrum from Keck/HIRES on the night of 2021 March 26 using the
%standard setup and reduction techniques of the California Planet
%Survey \citep{howard_cps_2010}.  Following the equivalent width
%measurement procedure described by \citet{bouma_2021_ngc2516}, we find
%${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
%given the stellar effective temperature (Table~\ref{tab:starparams}),
%this measurement is in agreement with expectations for a
%$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
%\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
%equivalent widths measured by \citet{berger_identifying_2018} in their
%analysis of 1{,}301 Kepler-star spectra.
%
%
%% rotation period from plot_rotation_period_windowslider.py
%Based on the spatial and kinematic association of \sn\ with the \cn,
%and the assumption that the planet formed shortly after the star, it
%seems likely that \sn\ is the same age as the cluster. There are two
%consistency checks on whether this is true: rotation and lithium.
%Based on the Kepler light curve, the rotation period is
%$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
%scatter in rotation periods measured from each individual Kepler
%quarter.  This is consistent with comparable cluster members
%(Figure~\ref{fig:age}).

%\subsection{Kepler\,1627A}
\subsection{Kepler\,1643}
\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.85\textwidth]{f3e.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.41\textwidth]{f3a.pdf}
			\includegraphics[width=0.41\textwidth]{f3b.pdf}
		}

		\vspace{-1.45cm}	
		\subfloat{
			\includegraphics[width=0.41\textwidth]{f3c.pdf}
			\includegraphics[width=0.41\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Raw and processed light curves for the objects of
    interest.} Top: raw.  Bottom: processed.
    The increased scatter during transit is likely due to starspot
    crossing events.  KOI-7913 is janky, but P=24 days.
		\label{fig:planets}
	}
\end{figure*}
